\section{AGM}

\begin{enumerate}

  \item Before the AGM the committee shall provide a document which outlines
    the activities and events which took place since the last AGM. This document
    should give members attending the AGM an insight into the activities
    of the society and give the new committee a guide to what they
    should go on to do in their term.

  \item All members shall be entitled to stand and to vote in elections.

  \item All members must receive at least 14 days written notification of the annual
    general meeting and of elections not held at the AGM.

  \item Motions to be discussed should be presented to the Secretary in advance of the AGM.

  \item The society shall also inform the EUSA Societies’ Office of the date, time and
    place of the society’s AGM.

  \item The AGM of the society must take place between week 7 and week 11 of
    semester 2.

  \item The quorum of a general meeting shall be 10\% of the current membership
    unless:-
    \begin{enumerate}
      \item The number of members is less than 50, in which case the quorum
        shall be 5 members.
      \item The number of members exceeds 200 in which case the quorum shall
        be 20 members.
    \end{enumerate}

  \item Votes shall be cast by the raising of hands, unless any member requests
    otherwise, in which case votes shall be cast by secret ballot.

  \item New Office Bearers must be assigned to the Society Profile immediately
    upon election.

  \item The following shall be the procedure for amending the constitution:-
    \begin{enumerate}
      \item The committee must make the amended constitution available to
        society members no later than 14 days prior to a general meeting.
      \item Suggested changes to an amended constitution must be submitted to
        the committee no later than two days prior to the general meeting.
      \item Changes to an amended constitution will be presented at the general
        meeting and will be voted upon. Changes to an amended constitution
        must be passed by a two third majority. After all changes have been
        voted on, the amended constitution with the passed changes will be
        voted on.
      \item The amended constitution must be passed with a two third majority
        at the general meeting.
    \end{enumerate}

  \item When elections are held there will always be an option to re-open nominations.
    This option will be presented as an additional candidate, “Ron”.
    If Ron gets the greatest amount of votes the position will be kept open
    and an EGM shall be called by the committee to fill the position.
    Nominations may be made at the AGM, subject to the nominee\textquotesingle s
    consent.

  \item If no nominations are received for any of President, Secretary or Treasurer,
    the incumbent committee shall call an EGM within 4 weeks. If all 3
    positions are not filled following an EGM, the incumbent committee shall
    inform EUSA that the society has become defunct. Anybody can reform
    the society by contacting EUSA, however this must be done within 3 years
    or all society assets will be lost.

\end{enumerate}
% End section 'AGM'
