\section{Miscellaneous Provisions}  
\subsection{Ethical Compliance}
CompSoc shall not engage in or endorse any activities which may bring the Society or University into legal or ethical disrepute, including but not limited to:  
\begin{enumerate}
    \item Discrimination, bullying or harassment of individuals or groups
    \item Fraud, bribery, embezzlement or other financial malfeasance  
    \item Violation of intellectual property rights
    \item Unauthorized hacking or other malicious technical activities
    \item Libel, slander, hate speech or other defamatory conduct
\end{enumerate}

\subsection{Dispute Resolution}  
\begin{enumerate}
    \item The CompSoc committee shall serve as the first point of contact for the good-faith resolution of all member disputes and grievances. 
    \item If the committee is unable to neutrally adjudicate a dispute, the matter shall be escalated to the EUSA Societies team for mediation.
    \item Only after exhausting the above internal resolution options may a CompSoc member pursue external legal action against the society or its officers.
\end{enumerate}

\subsection{Dissolution Provisions}
\begin{enumerate} 
    \item A motion to dissolve CompSoc and distribute its assets may only be passed by a two-thirds majority vote at an AGM or EGM, provided the membership has been given 14 days advance notice of this agenda item.
    \item Upon dissolution, any residual CompSoc funds and assets shall be transferred to the School of Informatics or another appropriate Informatics-related student initiative as determined by the committee.  
    \item The outgoing CompSoc President and Treasurer shall be responsible for the orderly winding-down of the society and closure or transfer of all banking accounts and assets within 60 days of dissolution.
\end{enumerate}

\subsection{Recognition of Governing Documents}
This constitution has been duly approved by the CompSoc membership as the binding authority governing the society's operations and conduct. The document shall be reviewed and re-ratified each academic year at the AGM, with the authoritative version displayed publicly on the official CompSoc website.